Study protocol

### 2021-12-23 Manuscript/S1.Protocol.Rmd
fixed a typo

selection_set <- generate_rule_selection_set(
	candidate_queries$rule,
	target_vec = Target,
	target_data = SpecificDTM)

selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')
openxlsx::write.xlsx(selection_set, selection_set_file)

@@

simplified_rules <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx') %>%
	import_data() %>%
	simplify_ruleset(ruleset = Target, SpecificDTM) %>%
	pull(rule)

>>>>

selection_set_file <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx')

selection_set <- generate_rule_selection_set(
	candidate_queries$rule,
	target_vec = Target,
	target_data = SpecificDTM,
	save_path = selection_set_file)

@@

simplified_rules <- file.path('Sessions', 'Session1', 'Selected_rules.xlsx') %>%
	import_data() %>%
	simplify_ruleset(target_vec = Target, target_data = SpecificDTM) %>%
	pull(rule)
